---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

**NOTE** Requires [`libplist`](https://github.com/libimobiledevice/libplist).

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(plist)

# current version
packageVersion("plist")

```

Plaintext XML property list in a string:

```{r xml-plist}
xml <- '<?xml version="1.0" encoding="UTF-8"?>
<!DOCTYPE plist PUBLIC "-//Apple//DTD PLIST 1.0//EN" "http://www.apple.com/DTDs/PropertyList-1.0.dtd">
<plist version="1.0">
<dict>
<key>Label</key>
<string>com.example.app</string>
<key>Program</key>
<string>/Users/Me/Scripts/cleanup.sh</string>
<key>RunAtLoad</key>
<true/>
</dict>
</plist>'

plist_to_list(xml)
```

Same content but binary property list:

```{r raw-plist}
as.raw(c(0x3c, 0x3f, 0x78, 0x6d, 0x6c, 0x20, 0x76, 0x65, 0x72, 
0x73, 0x69, 0x6f, 0x6e, 0x3d, 0x22, 0x31, 0x2e, 0x30, 0x22, 0x20, 
0x65, 0x6e, 0x63, 0x6f, 0x64, 0x69, 0x6e, 0x67, 0x3d, 0x22, 0x55, 
0x54, 0x46, 0x2d, 0x38, 0x22, 0x3f, 0x3e, 0x0a, 0x3c, 0x21, 0x44, 
0x4f, 0x43, 0x54, 0x59, 0x50, 0x45, 0x20, 0x70, 0x6c, 0x69, 0x73, 
0x74, 0x20, 0x50, 0x55, 0x42, 0x4c, 0x49, 0x43, 0x20, 0x22, 0x2d, 
0x2f, 0x2f, 0x41, 0x70, 0x70, 0x6c, 0x65, 0x2f, 0x2f, 0x44, 0x54, 
0x44, 0x20, 0x50, 0x4c, 0x49, 0x53, 0x54, 0x20, 0x31, 0x2e, 0x30, 
0x2f, 0x2f, 0x45, 0x4e, 0x22, 0x20, 0x22, 0x68, 0x74, 0x74, 0x70, 
0x3a, 0x2f, 0x2f, 0x77, 0x77, 0x77, 0x2e, 0x61, 0x70, 0x70, 0x6c, 
0x65, 0x2e, 0x63, 0x6f, 0x6d, 0x2f, 0x44, 0x54, 0x44, 0x73, 0x2f, 
0x50, 0x72, 0x6f, 0x70, 0x65, 0x72, 0x74, 0x79, 0x4c, 0x69, 0x73, 
0x74, 0x2d, 0x31, 0x2e, 0x30, 0x2e, 0x64, 0x74, 0x64, 0x22, 0x3e, 
0x0a, 0x3c, 0x70, 0x6c, 0x69, 0x73, 0x74, 0x20, 0x76, 0x65, 0x72, 
0x73, 0x69, 0x6f, 0x6e, 0x3d, 0x22, 0x31, 0x2e, 0x30, 0x22, 0x3e, 
0x0a, 0x09, 0x3c, 0x64, 0x69, 0x63, 0x74, 0x3e, 0x0a, 0x09, 0x09, 
0x3c, 0x6b, 0x65, 0x79, 0x3e, 0x4c, 0x61, 0x62, 0x65, 0x6c, 0x3c, 
0x2f, 0x6b, 0x65, 0x79, 0x3e, 0x0a, 0x09, 0x09, 0x3c, 0x73, 0x74, 
0x72, 0x69, 0x6e, 0x67, 0x3e, 0x63, 0x6f, 0x6d, 0x2e, 0x65, 0x78, 
0x61, 0x6d, 0x70, 0x6c, 0x65, 0x2e, 0x61, 0x70, 0x70, 0x3c, 0x2f, 
0x73, 0x74, 0x72, 0x69, 0x6e, 0x67, 0x3e, 0x0a, 0x09, 0x09, 0x3c, 
0x6b, 0x65, 0x79, 0x3e, 0x50, 0x72, 0x6f, 0x67, 0x72, 0x61, 0x6d, 
0x3c, 0x2f, 0x6b, 0x65, 0x79, 0x3e, 0x0a, 0x09, 0x09, 0x3c, 0x73, 
0x74, 0x72, 0x69, 0x6e, 0x67, 0x3e, 0x2f, 0x55, 0x73, 0x65, 0x72, 
0x73, 0x2f, 0x4d, 0x65, 0x2f, 0x53, 0x63, 0x72, 0x69, 0x70, 0x74, 
0x73, 0x2f, 0x63, 0x6c, 0x65, 0x61, 0x6e, 0x75, 0x70, 0x2e, 0x73, 
0x68, 0x3c, 0x2f, 0x73, 0x74, 0x72, 0x69, 0x6e, 0x67, 0x3e, 0x0a, 
0x09, 0x09, 0x3c, 0x6b, 0x65, 0x79, 0x3e, 0x52, 0x75, 0x6e, 0x41, 
0x74, 0x4c, 0x6f, 0x61, 0x64, 0x3c, 0x2f, 0x6b, 0x65, 0x79, 0x3e, 
0x0a, 0x09, 0x09, 0x3c, 0x74, 0x72, 0x75, 0x65, 0x2f, 0x3e, 0x0a, 
0x09, 0x3c, 0x2f, 0x64, 0x69, 0x63, 0x74, 0x3e, 0x0a, 0x3c, 0x2f, 
0x70, 0x6c, 0x69, 0x73, 0x74, 0x3e, 0x0a)) -> raw_plist

plist_to_list(raw_plist)
```

Raw, unparsed XML vs a list:

```{r uparsed-xml}
plist_to_xml(xml)

plist_to_xml(raw_plist)
```

From files:

```{r from-files}
# plaintext XML
read_plist(system.file("sample/plist.txt", package = "plist"))

# binary
read_plist(system.file("sample/plist.bin", package = "plist"))
```

## plist Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
